---
title: "Sharafi_HW8"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Question 2
**Tutorial steps for Strings from Chapter 14**
**14.2.5 #3**
There are two approaches to deal with even numbers since we do not have a middle letter on them. I wrote both of the possible ways.
```{r}
library(tidyverse)
x <- c("Apple", "Banana", "Pear")
str_sub(x,(str_length(x)+1)/2, (str_length(x)+1)/2) # Choose integr before middle 
str_sub(x,ceiling((str_length(x)+1)/2), ceiling((str_length(x)+1)/2))#choose integer after middle 

```
**14.2.5 #4**
Format a string by warping the text and modifying width and indentation.WHen we have a long text in string data.

**14.2.5 #5**
Eliminate spaces at the beginning or end of a string. Remove the vacant spaces between text and quotation on both sides. 

**14.2.5 #6**
Function that turns  a vector into the string
```{r}
string_maker <- function(x){n <- length(x)
y <- c()
# Create a particular condition when the length of the vector is 0,1,2
  if (n == 0) {
    NULL
  }else if  (n == 1){
  str_c(" ", x, " ")
}else if  (n == 2){
  str_c(" ",x[[1]], ",and", x[[2]]," ",sep =" " )}
else {
  for(i in 1:(n-1)){y <- str_c(y," ",x[[i]],",")}
  y <- str_c(y," and"," ",x[[n]])
  y
}
}
```
**14.3.1.1 #3**

"\\..\\..\\..", we know that "\\." will match with "." and then another "." can represent any character so it will be something like the following:
```{r}
str_view(c(".a.a.a","abc", "a.b"), "\\..\\..\\..")
```

**14.3.3.1 #1**
**1.**Start with a vowel.
```{r}
str_view(c("why","apple","enter","booked","nine","item"),("^[aeiou]"))
```
**2.**That only contain consonants. 
```{r}
str_view(c("why","apple","enter","booked","nine","item"), "^[^aeiou]+$")
```
**3.**d with ed, but not with eed.
```{r}
str_view(c("why","apple","entering","booked","nine","item","seed"),"[^e]ed$")
```
**4.**End with ing or ise
```{r}
str_view(c("why","apple","entering","booked","nine","item","seed","wise"),"[i](se|ng)$")
```
**14.3.4.1 #2**
**1.**^.*$This is going to match whatever It's there
**2.**`"\\{.+\\}"`At least one character inside of  curly braces
**3.**`\d{4}-\d{2}-\d{2}` It is lookate like the date format 2020-22-03
**4.**"\\\\{4}" ,it is expressing "\\\\\\\\" but mine is not working with ''

**14.4.3.1 #2**

```{r}
#define the contractions
contract <- "([A-Za-z]+)'([A-Za-z]+)"
ans <-  str_extract(sentences, contract) %>% na.omit() %>% str_split("'",simplify = TRUE)
ans
```

**14.4.4.1 #1**
Replace all forward slashes in a string with backslashes.
```{r}
str_replace_all("c/desktop/es207/hw/hw2", "/", "\\\\")
```

**14.4.5.1 #1**

```{r}
x <- c("apples, pears, and bananas") 
x <- str_split(x, ",|and")
x
```

**14.4.5.1 #2**
'" "' expression keeps the spaces as blank and also holds punctuation.
**14.5.1 #2**
What are the five most common words in sentences?

**14.5.1 #2**

```{r}

word <-  unlist(str_extract_all(sentences, boundary("word")))
word <- tibble(word) %>%
  mutate(word = str_to_upper(word)) %>%
  count(word, sort = TRUE)
word 
```
It looks like all of them are propositions

## Data Wrangling of CA Air Quality Data
```{r, , include=FALSE}
library(tidyverse, quietly = TRUE)
library(readr, quietly = TRUE)
o3.filepaths <- list.files("~/Documents/es_207_hw8", "\\.txt$", full.names = TRUE)
o3.filenames <- list.files("~/Documents/es_207_hw8", pattern = ".txt") # check your dirs
o3.filelist <- lapply(o3.filepaths, read_delim, delim = "|")
names(o3.filelist) <- gsub(".txt","", o3.filenames)
o3.filelist
```
## Question 3

```{r}
class(o3.filelist)
```
The class of "o3.filelist" is the List format in 10 rows of information, which are capture from 10 files from 1881 to 2011.  however, each row divided into four subsections row. Besides the columns for name, there are two columns, one in Tibble the in List, which I think they have the same information just in different formats. 

## Question 4
After activating tidyverse, and reader.
**1** o3.filepaths <- list.files("lectures/data/ca_ozone", "\\.txt$", full.names = TRUE)
In code line **1**, we list the path of the all data file that we want to use in "o3.filepaths"
**2**o3.filenames <- list.files("lectures/data/ca_ozone", pattern = ".txt") 
Then collect all teh file name in file and Called it "o3.filenames"
**3** o3.filelist <- lapply(o3.filepaths, read_delim, delim = "|")
After that, with the help of function "lapply" , the main data file was created.use function to read_delim to save them in tibble format. 
**4** names(o3.filelist) <- gsub(".txt","", o3.filenames)
Then with 'gsub' the filenames were replaced and delete, it means the".txt" from the filenames

## Question 5
Useing str_replace instead of gsub
```{r}
names(o3.filelist) <- str_replace(string = o3.filenames, pattern = ".txt", replacement = "") 
```

## Question 6

```{r, include=FALSE}
# first define my function
o3summarize <- function(x){
  out <- group_by(x, site = as.factor(site), date) %>%
  summarize(o3 = mean(obs, na.rm = TRUE))
}
# now apply my function to the list of tibbles
daily <- o3.filelist %>% 
  map(o3summarize)
daily
```
Some Data Wrangling to obtained the 
```{r}
daily3 <- daily[[3]]
daily3 <- as.tibble(daily3)
library(lubridate)
daily3$year <- year(daily3$date)
daily3$month <- month(daily3$date)
monthly.o3 <- daily3 %>% select(site, year, month,o3) 
monthly.o3
```

## Question 7
Ozone is generally assumed to have weak diurnal variations, so regards our data collected daily, I added day column to the data frame
```{r}
daily3$day <- day(daily3$date)
daily.o3 <- daily3 %>% select(site, year, month,day,o3) 
daily.o3
```

## Question 8
```{r}
library(readxl)
loc <- read_excel("~/Documents/es_207_hw8/location.xls")
z <- loc$`Site Name`
z = str_to_upper(z)
z <- as.tibble(z)
NameSan<- str_count(z,"SAN|SANTA")
print(paste("Number of name of sites with -SAN- in it:",NameSan))

```

## Question 9

```{r}
loc1 <- loc[!is.na(loc$`Zip Code`), ]
Adress.check <- str_count(as.tibble(loc1$Address),"Location Approximate")
Complete.adress <- length(loc1$`Zip Code`)-Adress.check
print(paste("Number of site with complete adress:",Complete.adress))
```
## Question 10
We  can make a dataset tidy by applying these three golden rules:
Each variable must have its own column.
Each observation must have its own row.
Each value must have its own cell
'tidyverse' is a package that has useful tools to help tidy up our messy datasets. 
ref:<https://r4ds.had.co.nz/tidy-data.html>

## Question 11
They interrelated since it’s impossible only to satisfy two of the three. That interrelationship leads to an even more straightforward set of practical guidance.
ref:<https://r4ds.had.co.nz/tidy-data.html>

## Question 12

```{r, include=FALSE}
library(data.table)
daily.tibble <- rbind_list(daily)
colnames(loc)[1] <- "site"
daily.site <- daily.tibble %>%left_join(loc, by = "site")

```
I am going to write a function for obtaining an annual mean of daily mean, which you determined in the past and stored it in 'daily'.
```{r}
# new annual mean fucntion
o3year <- function(x){
    out <- group_by(x, site = as.factor(site), year) %>%
  summarize(o3 = mean(o3 , na.rm = TRUE))
}
```

```{r}
daily.site$year <- year(daily.site$date)
yearly <-  group_by(daily.site, site = as.factor(site), year)%>% summarize(o3 = mean(o3 , na.rm = TRUE))
head(yearly)
```
Know for visualization we plot the data
```{r}
loc_merced <- loc %>% filter(`County Abbr`== "MER")
q <- loc_merced$site
yearly_merced <- yearly %>% filter(site%in% q)
yearly_merced <-yearly_merced %>% filter(site=="3022")
ggplot(yearly_merced, aes(x=year, y=o3)) + 
  geom_point()
```
and then gather all the data in the table
```{r}
knitr::kable(
  yearly_merced[,2:3 ], caption = 'The annual daily mean of o3 for Merced County.'
)
```
## Question 13


```{r}
#Specify it for Merced county
daily.site.merced <- daily.site%>% filter(site%in% "3022") # I chose one stataion in merced
#make a daily 
daily.merced <- daily.site.merced  %>% select(site,o3,date,year) %>% na.omit()
daily.merced$time <- seq(1,length(daily.merced$date))
# i make time series of day
Day <- daily.merced $time # for the sake of cleanliness
o3 <- log(daily.merced $o3)
loess25 <- loess(Day~o3, degree = 2, span = 0.25) # 50% smoothing span
#plot time series quadratic
g <- ggplot(daily.merced , aes(x = Day, y = o3,color=year))+ 
  geom_point(alpha = 0.2, na.rm = T)
g <- g +   
   geom_smooth(method = "loess", span = 0.25,method.args = list(degree=2), se = FALSE,color = "blue", na.rm = T)
g

```
Definitely, there is a seasonal trend 


## Question 14

```{r}
#stl(loess25, s.degree = 0)
#error:  Error in complete.cases(object) : not all arguments have the same length
```


